Replication Survey

### 2023-07-26 docs/manuscript/manuscript.tex
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
A total of \textit{n}=283 of the authors we contacted completed the online survey with information sufficient for analysis. 
The contact rate for the survey was 17.7 percent, the response rate was 11.3 percent, yielding a cooperation rate of 64.0 percent. 
The refusal rate was 6.4 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}.
Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
The majority of respondents were also academics, but were well balanced across career levels as no one category made up more that 30 percent of the sample.
Respondents were similarly balanced across disciplinary subfields, but did contain a greater number of physical geographers  - human geography (26.8\%), physical geography (39.9\%), nature and society (14.8\%), geographic methods and GIScience (17.3\%). 
Different methodological approaches were well represented by respondents in the sample with qualitative researchers making up the smallest sub-group  - quantitative (47.3\%), qualitative (16.3\%), and mixed-methods (36.0\%).

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Replication - Chances and motivations}
Overall geographic researchers believe that the majority of research in the discipline has not been independently replicated and appear to be uncertain about what proportion of literature could or should be replicated (Figure \ref{fig:Q12-HCS}). 
On average, respondents estimated that 25 percent of recent studies in their sub-field have be replicated. 
However, this average likely overstates the percentage of studies researchers believe have been replicated because the response distribution is strongly right skewed.
Our median response to this question is 20 percent and a heavy tail of containing 46.9 percent of responses estimated that less than 10 percent of recent studies have been replicated.
On average, respondents estimated that approximately half of studies 'could be replicated' (55.0\%) or 'should be replicated' (55.9\%). 
However, these averages are the product of the relatively flat distributions of estimates across the range of possible values. 
The response to both questions was also highly variable (\textit{$sd_{could}=24.3\%$}, \textit{$sd_{should}=27.7\%$}) indicating no common knowledge or belief about the possibility or value of replicating recent work.

@@

Q8-11 Factors that affect the chances of replicating a claim.
Researchers collectively indicated that only a few study characteristics of phenomenon characteristics would alter an independent researcher's chances of replicating a prior claim. 
Researcher identified more study characteristics than phenomena characteristics, which may indicate they they are thinking of this through the lens of artifact availability from the prior study and not the nature of the phenomena. 
A small but notable percentage of researchers indicated that they simply did not know whether a factor would affect chances of replication.

Only a subset of study characteristics were consistently identified by geographic researchers as altering the chances of replicating the claims of a prior study.
\begin{itemize}
    \item Agreement that quantitative studies are more likely to be replicable (80.6\%)
    \item Poor documentation decreases chances of replication (74.9\%)
    \item use of restricted data decreases chances (68.1\%)
    \item Positionality seemed to give a lean to decrease (53.4\%)
    \item Researcher views on most study characteristics were fairly evenly split across increase, decrease, no-effect. Indicating they were not seen as consistently important across the the discipline. 
    \item Minimal variation in responses across method groups or sub-fields. 
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Factors that Affect the Decision to Attempt Replications}
Figure \ref{fig:Q15-DecisionFactors} presents how frequently geographic researchers believe differences in academic incentives (AI), the availability of research artifacts (AA), and study characteristics (SC) affect the decision to attempt to replicate existing geographic research.
We highlight how often researchers identified a given factor as always or frequently influencing the decision to attempt a replication study and use a 50 percent threshold to indicate factors identified as important by a majority of respondents. 
Item response rate are included at the right of the figure.

@@

Geographic researchers identified current academic incentives as the factor most frequently impacting the decision to attempt or not attempt a replication study. 
A majority of respondents identified the pressure to publish original research (77\%) and the lack of funding for replication studies (73\%) as frequently or always impacting the replication decision.
Respondents also believed that the perception of replications as low value work (64\%) that was often difficult to publish (63\%) impacted researcher decision making.  
Contrary to some narratives in the replication literature, the desire to identify fabricated data or results was not seen as a determining factor in the decision to attempt a replication. 
However, this finding should be interpreted with caution as a third of our respondents indicated that they did not know whether potential fabrication influenced researcher decision making.

Survey respondents also identified the availability of research artifacts as another set of factors impacting the decision to attempt replications of geographic research.
Difficulty accessing and recreating data was the most commonly identified deterrent of replication with 61 percent of respondents naming this factor as frequently or always affecting the replication decision.
Similarly, a slight majority of respondents (51\%) identified the accessibility of procedural and methodological information as a influencing factor. 
The challenge of recreating the methods of a prior study elicited a similar response (47\%).

No characteristics of the original study, or the potential replication attempt, were identified by a majority of researchers as frequently or always impacting the replication decision. 
However, a near majority of respondents did identify potential geographic variation in the phenomena being investigated (43\%) and inexperience conducting replication studies (45\%) as influencing researcher decisions to attempt or not attempt replications. 
Respondents did not see a low chance of successfully replicating a study as a deterrent to attempting a replication, but it is unclear whether this result is driven by a belief in the value of null replication results or the belief that replications in fact have high chances of success.
Finally, researchers did not identify ethical concerns as a factor affecting the decision to attempt a replication study.

Respondents also identified a number of factors that were omitted from our survey instrument. 
These factors include practical issues such as the difficulty identifying and accessing new field sites where data would be collected during a replication attempt, the costs of conducting a replication, and the time needed to obtain institutional approvals.
Selected respondents also identified uncertainty about how to compare the  of results of a replication and an prior study as a factor impacting the decision to attempt a replication. 
Finally, a small number of respondents believe that geographic researchers do not undertake replication studies because they either believe replication is not possible or not necessary in geography. 
These researchers argued that the main value of geographic studies is that each study provide a unique lens on the portion of the world under investigation, which makes replication a unnecessary endeavour.

Respondents from different disciplinary sub-fields and methodological approaches varied little in their identification of the factors affecting researchers' decisions to attempt a replication studies. 
Human geographers and researchers using quantitative methods less frequently identified academic incentives as important to the replication decision when compared to other sub-groups, but were otherwise broadly similar in their views on artifact availability and study characteristics. 
A greater percentage of quantitative researchers and those working in the areas of GIScience and Methods identified the accessibility of data and methodological information as more commonly impacting the decision to replicate, but not at a level that was substantially higher than other sub-groups. 
In fact, a greater percentage of researchers studying nature and society identified data accessibility as important than did methods researchers.  
Overall, the differences we observed across sub-groups was small and should be interpreted with caution given the sub-group sample sizes.
We also found that human geographers and qualitative researchers were disproportionately likely to provide 'I do not know' responses across questions,  
which further decreases the amount of information available about their views and beliefs.

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=0.8]{results/figures/Fig-Q8-10-Chances.png}
    \caption{Factors affecting the chances of replicating a study. Respondents identified (a) how likely study characteristics were to alter the chances of successfully replicating a study and (b) how likely the characteristics of the phenomenon under investigation were to alter the chances of successfully replicating a study in a new location. Acronyms indicate: artifact accessibility (AA), researcher characteristics (RC), study approach (SA), and phenomenon characteristics (PC); and the percentage of 'don't know' (DK) and missing (M) responses. Unlikely to affect replication chances is omitted, but can be calculated from available data.}
    \label{fig:Q8-10-Chances}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
A total of \textit{n}=283 of the authors we contacted completed the online survey with information sufficient for analysis. 
The contact rate for the survey was 18.8 percent, the response rate was 14.1 percent, yielding a cooperation rate of 74.4 percent. 
The refusal rate was 4.8 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}.
Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
The majority of respondents were also academics, but were well balanced across career levels as no one category made up more that 30 percent of the sample.
Respondents were similarly balanced across disciplinary subfields, but did contain a greater number of physical geographers  - human geography (26.8\%), physical geography (39.9\%), nature and society (14.8\%), geographic methods and GIScience (17.3\%). 
Different methodological approaches were well represented by respondents in the sample with qualitative researchers making up the smallest sub-group  - quantitative (47.3\%), qualitative (16.3\%), and mixed-methods (36.0\%).

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Replication - Chances and motivations}
Overall respondents believe that the majority of research in the discipline has not been independently replicated and appear to be uncertain about what proportion of the literature could or should be replicated (Figure \ref{fig:Q12-HCS}). 
On average, respondents estimated that 25 percent of recent studies in their sub-field have be replicated. 
However, the distribution of these responses is strongly right skewed.
In fact, 46.9 percent of respondents estimated that less than 10 percent of recent studies have been replicated.
It is unclear if respondents believe recent geographic research could or should be replicated.
On average, respondents estimated that approximately half of studies 'could be replicated' (55.0\%) or 'should be replicated' (55.9\%). However, the distribution of responses to both questions are relatively flat across the range of possible values and highly variable (\textit{$sd_{could}=24.3\%$}, \textit{$sd_{should}=27.7\%$}), which suggests 
respondents were uncertain whether it was possible or valuable to replicate recent research.

@@

Respondents identified a range of factors that might impact the chances of an independent researcher replicating the claims of a prior study (Figure \ref{fig:Q8-10-Chances}a).
A majority of respondents identified the transparency and availability of the components of a study as affecting the odds of replication. 
Poor documentation of the original study (75\%) and the use of restricted access data (68\%) were seen by the greatest number of respondents as decreasing the odds of replication. 
Some respondents identified the inclusion of multiple sites in a study as increasing the chances of an independent replication of the findings of that study, but not in great enough numbers to constitute a majority.

The characteristics of the research team that conducted the original study were generally not identified by respondents as likely to change the changes of replicating that study. 
Respondents were nearly evenly split as to whether a large research team working on a study increased of decreased the chances of replicating that study. 
On the whole, more respondents believed that reliance on the unique expertise of the research team conducting a study, or the position adopted by that team would decrease, rather than increase, the chances of replicating the claims of a study.
However, only 54 percent of respondents thought the position a research team chose to adopt when conducting study would decrease the chances of replicating that study. 
Similarly, 49 percent of respondents identified reliance on the unique expertise of the original researcher team as decreasing the odds of replicating a study.

\vspace{5mm}

Researcher identified more study characteristics than phenomena characteristics, which may indicate they they are thinking of this through the lens of artifact availability from the prior study and not the nature of the phenomena. 
A small but notable percentage of researchers indicated that they simply did not know whether a factor would affect chances of replication.

Only a subset of study characteristics were consistently identified by geographic researchers as altering the chances of replicating the claims of a prior study.
\begin{itemize}
    \item Agreement that quantitative studies are more likely to be replicable (80.6\%)
    \item Minimal variation in responses across method groups or sub-fields. 
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Factors that Affect the Decision to Attempt Replications}
Several factors appear to affect whether researchers decide to attempt to replicate recent geographic research.
Figure \ref{fig:Q15-DecisionFactors} presents how frequently respondents believe differences in academic incentives (AI), the availability of research artifacts (AA), and study characteristics (SC) affect researchers' decisions to attempt to replicate existing geographic research.
Response characteristics for each factor are recorded at the right of the figure.

@@

Geographic researchers identified current academic incentives as the factor most frequently impacting the decision to attempt a replication study. 
A majority of respondents identified the pressure to publish original research (77\%) and the lack of funding for replication studies (73\%) as frequently or always impacting the decision to attempt a replication.
Respondents also believed that the perception of replications as low value work (64\%) that was often difficult to publish (63\%) also impacted decision making.  
Contrary to some narratives in the replication literature, the desire to identify fabricated data or results was not seen as a determining factor in the decision to attempt a replication. 
However, this finding should be interpreted with caution as a third of respondents indicated that they did not know whether potential fabrication influenced researcher decision making.

Respondents also identified the availability of research artifacts as important to the decision to attempt a replication study.
Respondents believe that difficulty accessing and recreating data (61\%) frequently or always affects the replication decision.
Similarly, a slight majority of respondents (51\%) identified the accessibility of procedural and methodological information as a influential factor. 
The challenge of recreating the methods of a prior study elicited a similar response (47\%).

No characteristics of the original study, or the potential replication attempt, were identified by a majority of researchers as frequently or always impacting the replication decision. 
However, a near majority of respondents did identify potential geographic variation in the phenomena being investigated (43\%) and inexperience conducting replication studies (45\%) as influencing decisions to attempt replications. 
Respondents did not see a low chance of successfully replicating a study as a deterrent to attempting a replication, but it is unclear whether this result is driven by a belief in the value of null replication results, or the belief that replications in fact have high chances of success.
Finally, respondents did not identify ethical concerns as a factor affecting the decision to attempt a replication study.

Respondents identified a number of factors that were omitted from our survey instrument as important when deciding whether to attempt a replication of a geographic study. 
These factors include practical issues such as the difficulty identifying and accessing new field sites where data would be collected during a replication attempt, the costs of conducting a replication, and the time needed to obtain institutional approvals.
Respondents also identified uncertainty about how to compare the results of a replication attempt to the original as important to the replication decision.. 
Finally, a small number of respondents believe that geographic researchers do not undertake replication studies because those researchers either believe replication is not possible or not necessary in geography. 
These respondents argued that the main value of geographic studies is that each study provide a unique lens on the portion of the world under investigation, which makes replication a unnecessary endeavour.

Respondents from different disciplinary sub-fields and methodological approaches varied little in their identification of the factors affecting researchers' decisions to attempt replication studies. 
Human geographers and researchers using quantitative methods less frequently identified academic incentives as important to the replication decision when compared to other sub-groups, but were otherwise broadly similar in their views on artifact availability and study characteristics. 
A greater percentage of quantitative researchers and those working in the areas of GIScience and Methods identified the accessibility of data and methodological information as more often impacting the decision to replicate, but not at a level that was substantially higher than other sub-groups. 
In fact, a greater percentage of researchers studying nature and society identified data accessibility as important than did methods researchers.

Overall, the differences we observed across sub-groups was small and should be interpreted with caution given the sub-group sample sizes.
We also found that human geographers and qualitative researchers were disproportionately likely to provide 'I do not know' responses across questions,  
which further decreases the amount of information available about their views and beliefs.

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=0.8]{results/figures/Fig-Q8-10-Chances.png}
    \caption{Factors affecting the chances of replicating a study. Respondents identified (a) how likely study characteristics were to alter the chances of successfully replicating a study and (b) how likely the characteristics of the phenomenon under investigation were to alter the chances of successfully replicating a study in a new location. Acronyms indicate: artifact accessibility (AA), researcher characteristics (RC), study approach (SA), and phenomenon characteristics (PC); and the percentage of `don't know' (DK) and missing (M) responses. Unlikely to affect replication chances is omitted, but can be calculated from available data.}
    \label{fig:Q8-10-Chances}
\end{figure}
